%-----------------------------------------------------------------------------------------------------------------------------------------------%
% Based on autoCV by Jitin Nair
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,9pt]{article}

\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[margin=0.45in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[unicode, draft=false]{hyperref}

\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\titleformat{\section}{\normalsize\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{3pt}
\setlist[itemize]{nosep, leftmargin=1em, itemsep=1pt, label=\textbullet}
\setlength{\parskip}{1pt}
\pagestyle{empty}

\newenvironment{role}[4]
    {
    \noindent\textbf{#1}\\[-1pt]
    \begin{tabularx}{\linewidth}{@{}L R{1.75in}@{\hspace{1em}}R{1.35in}@{}}
    \textit{#3} & #2 & \textit{#4} \\[-2pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
    }
    {
    \end{itemize}
    \end{minipage}
    \par\vspace{3pt}
    }

\newenvironment{projectentry}[2]
    {
    \begin{tabularx}{\linewidth}{@{}L r@{}}
    \textbf{#1} & #2 \\[-2pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}
    }
    {
    \end{itemize}
    \end{minipage}
    \par\vspace{3pt}
    }

\begin{document}

\begin{tabularx}{\linewidth}{@{} C @{}}
\huge{\textbf{Edward Joshua M. Diesta}} \\[3pt]
Quezon City, Philippines \ $|$ \
\href{tel:+639693145003}{+63 969 314 5003} \ $|$ \
\href{mailto:edwardjoshua.diesta@gmail.com}{edwardjoshua.diesta@gmail.com} \ $|$ \
\href{https://edwarddiesta.com}{edwarddiesta.com} \ $|$ \
\href{https://github.com/DrawdEA}{github.com/DrawdEA}
\end{tabularx}

\section{Education}
\begin{tabularx}{\linewidth}{@{}L r@{}}
\textbf{Ateneo de Manila University} & Expected May 2028 \\
\textit{BS Computer Science} \ $|$ \ QPI: 3.81/4.00 \ $|$ \ Magna Cum Laude standing & \\
\multicolumn{2}{@{}L@{}}{Scholarships: Ateneo Freshman Merit Scholar (top 60/10,000+); DOST-SEI Merit Scholar}
\end{tabularx}

\section{Experience}
\begin{role}{Bytespace Labs}{Remote, San Francisco, CA}{Product Engineer, Full-time}{May 2026 -- Present}
\item Shipped 21 Bot0 Desktop engineering changes across Electron UX, cross-platform reliability, artifact editing, integrations, and performance.
\item Led Windows parity work across automation surfaces, hardware-backed signing, permissions, local dev parity, packaging, and release readiness.
\item Built reusable artifact quick-edit infrastructure for reports, slides, and carousel previews, persisting edits into artifact state for preview/export generation.
\item Fixed desktop performance and usability issues in large diff rendering, workspace output expansion, session switching, Markdown export, and responsive UI surfaces.
\end{role}
\begin{role}{SOFI AI Tech Solution Inc.}{Quezon City, Philippines}{AI Developer Intern}{Dec 2025 -- Feb 2026}
\item Built an internal QA interface for reviewing and evaluating AI chat outputs, helping the team iterate faster on model behavior.
\item Developed frontend tooling with Vue.js and worked across LLM and retrieval-augmented generation pipelines.
\end{role}
\begin{role}{Sip \& Scale}{Quezon City, Philippines}{Software Engineer, Part-time}{Feb 2026 -- Present}
\item Developed and maintained the startup's public-facing website with Next.js, supporting the team's go-to-market presence.
\end{role}
\begin{role}{Ateneo Management Information Systems Association}{Quezon City, Philippines}{AVP for IT Skills and Development}{Jul 2025 -- Present}
\item Headed internal engineering initiatives and web development training for 20+ student developers.
\item Oversaw external client projects to give members hands-on experience building production-style web applications.
\end{role}

\section{Projects}
\begin{projectentry}{Crystal}{Apr 2026}
\item Built an AI-powered institutional memory platform with a knowledge graph dashboard and natural language query interface, ingesting Slack and Google Drive communications into Neo4j and pgvector with an async pipeline and real-time Slack bot.
\end{projectentry}
\begin{projectentry}{Project Agila: Multi-Tenant Digital Document Approval System}{Aug 2025 -- Present}
\item Developed a multi-tenant approval and review system with configurable workflows, role-based access control, drag-and-drop form building, auditor views, real-time messaging, and notifications using Next.js, React, TypeScript, and Supabase.
\end{projectentry}
\begin{projectentry}{MISA Registration \& Voting System}{Aug 2025 -- Mar 2026}
\item Collaborated with a team to build a registration and voting platform for 525 MISA members, reducing check-in time by 75\% across 15+ events using Next.js, React, Node.js, and PostgreSQL.
\end{projectentry}
\begin{projectentry}{LoClock}{Jan 2026 -- Present}
\item Built a React Native/Expo commute alarm app that triggers alerts based on GPS proximity instead of time, with background location tracking, push notifications, EAS builds, and OTA updates.
\end{projectentry}

\section{Hackathons and Awards}
\begin{itemize}
\item \textbf{Hakot}: 1st Runner Up, Ship or Be Shipped; built an AI agricultural logistics platform for return-trip load matching.
\item \textbf{Salbar}: Top 5 of 200+ teams, Naga City's 1st Mayoral Hackathon; built an offline-first emergency protocol with AI-assisted triage.
\item \textbf{Fortress}: Top 10, IM Summit IT Business Case Competition; proposed a FIDO2-based risk observation and security scoring system.
\end{itemize}

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Tech} & Next.js, React, TypeScript, JavaScript, Electron, React Native/Expo, Node.js, Python, PostgreSQL, Supabase, Prisma, Convex, Neo4j, pgvector, Git, GitHub, LLMs, RAG, Claude Code, Codex, C \\
\textbf{Lang/Certs} & English, Tagalog \ $|$ \ Machine Learning Specialization, DeepLearning.AI/Stanford \ $|$ \ CS50, Harvard/edX \\
\end{tabularx}

\end{document}
